A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-11 sanity/paper1.tex
Site Aidan's desiderata
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1050 43ef1190-90fd-4dd7-a769-d0121f02b80e
Reintroduce cuts
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1051 43ef1190-90fd-4dd7-a769-d0121f02b80e

Linked Data Fragments is claimed in \cite{ldf1} to take advantage of
caching and contrasts this with the unavailability of SPARQL query
caches, and it is claimed that this is an architectural problem.

@@

\todo{reintroduce refs} \todo{add Aidan's desiderata}

@@

In Figure~\ref{fig:hardall}, there is a barplot where
the freshness lifetime is grouped in bins. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days\todo{explain number of occur; fix labels}.

>>>>

Linked Data Fragments is claimed in \cite{ldf1} to take advantage of
caching and contrasts this with the unavailability of SPARQL query
caches, and it is claimed that this is an architectural problem. In
\cite{hogan2014paths}, the authors examine cacheable as one of the
desiderata for sustainable data access. They claim, without further
justification, that SPARQL isn't cacheable.

@@

@@

In Figure~\ref{fig:hardall}, there is a barplot where
the freshness lifetime is grouped in bins. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days\todo{explain number of occur; fix labels}\todo{qqplot in report}.
